# <b>[Full Season](https://en.wikipedia.org/wiki/2022_Formula_One_World_Championship)</b> {-}

```{r libraries, warning=FALSE, include=FALSE}
library(f1Package)
lapply(f1_reqPackages, require, character.only = TRUE) 
```

```{r include=FALSE}
round_var <- getLatestRound("data/latestRound.RDS")
target_year <- 2022
```

```{r include=FALSE}
# Grand Prix Rounds
url <- "http://ergast.com/api/f1/current"

temp <- xmlToList(rawToChar(GET(url)$content))

grandPrixRounds <- data.frame()
for(i in 1:(length(temp$RaceTable)-1)) {
  circuit_temp <- temp$RaceTable[i]
  
  row_temp <- cbind(
    as.numeric(circuit_temp$Race$.attrs["round"]),
    bind_rows(circuit_temp$Race[c(1,3)]),
    circuit_temp$Race$Circuit$CircuitName,
    bind_rows(circuit_temp$Race$Circuit$Location[1:2]),
    bind_rows(circuit_temp$Race$Circuit$Location$.attrs),
    circuit_temp$Race$.attrs["url"]
  ) %>%
    rename(
      CircuitName = "circuit_temp$Race$Circuit$CircuitName",
      Round = "as.numeric(circuit_temp$Race$.attrs[\"round\"])",
      url = 'circuit_temp$Race$.attrs["url"]'
      )
  
  grandPrixRounds <- rbind(grandPrixRounds, row_temp)
}

grandPrixRounds <- grandPrixRounds %>%
  mutate(pointsFirst = ifelse(
    Locality %in% c(
      "Imola",
      "Spielberg",
      "São Paulo"
    ),
    32,
    26
  )) %>%
  mutate(pointsSecond = ifelse(
    Locality %in% c(
      "Imola",
      "Spielberg",
      "São Paulo"
    ),
    25,
    20
  )) %>%
  mutate(pointsThird = ifelse(
    Locality %in% c(
      "Imola",
      "Spielberg",
      "São Paulo"
    ),
    21,
    15
  )) %>%
  mutate(lat = as.numeric(lat), long = as.numeric(long))
```

```{r message=FALSE, warning=FALSE, include=FALSE}
getDriverResult <- function(latestRound = latest_round) {
  
  if(!file.exists("data/driverResult2022.RDS")) {
    driverResult <- data.frame()
    max_round <- 1
  } else {
    driverResult <- readRDS("data/driverResult2022.RDS")
    max_round <- (max(driverResult$Round)+1)
  }
  
  if(max_round <= latestRound) {
    for(i in max_round:latestRound) {
      url <- paste("http://ergast.com/api/f1/current/", i, "/results", sep = "")
      
      temp <- rawToChar(GET(url)$content)
      
      while(temp == "Unable to select database") {
        temp <- rawToChar(GET(url)$content)
      }
      
      temp <- xmlToList(temp)
  
      driverResult_GP <- data.frame()
      for(j in 1:length(temp$RaceTable$Race$ResultsList)) {
        driverResult_ind <- temp$RaceTable$Race$ResultsList[j]
        result_temp <- cbind(
          bind_rows(driverResult_ind$Result$Driver[1:3]),
          bind_rows(driverResult_ind$Result$Driver$.attrs[1:2]),
          bind_rows(driverResult_ind$Result$Constructor[1]) %>% rename(Constructor = "Name"),
          bind_rows(driverResult_ind$Result$.attrs[c(2,4)]),
          bind_rows(driverResult_ind$Result[3:4]) %>% mutate(Grid = as.numeric(Grid), Laps = as.numeric(Laps)) %>% rename(StartingPos = Grid),
          bind_rows(driverResult_ind$Result$Status[1]) %>% rename(Status = text),
          if(is.null(driverResult_ind$Result$Time$.attrs)) {tibble(Time_sec = NA)} else {
            bind_rows(driverResult_ind$Result$Time$.attrs) %>% mutate(millis = as.numeric(millis) / 1000) %>% rename(Time_sec = millis)
          },
          if(is.null(driverResult_ind$Result$FastestLap[1])) {tibble(FastestLap = NA)} else {
            bind_rows(driverResult_ind$Result$FastestLap[1]) %>% mutate(Time = as.numeric(str_split(Time, ":")[[1]][1]) * 60 + as.numeric(str_split(Time, ":")[[1]][2])) %>% rename(FastestLap = Time)
          },
          if(is.null(driverResult_ind$Result$FastestLap$.attrs[1])) {tibble(rank = NA)} else {
            bind_rows(driverResult_ind$Result$FastestLap$.attrs[1]) %>% mutate(rank = as.numeric(rank))
          },
          if(is.null(driverResult_ind$Result$FastestLap$AverageSpeed[1])) {tibble(avgSpeedKph = NA)} else {
            bind_rows(driverResult_ind$Result$FastestLap$AverageSpeed[1]) %>% mutate(text = as.numeric(text)) %>% rename(avgSpeedKph = text)
          }
        ) %>%
          mutate(Round = i) %>%
          relocate(Round, .before = position) %>%
          mutate(
            StartingPos = ifelse(StartingPos == 0, NA, StartingPos),
            FullName = paste(GivenName, FamilyName)
          ) %>% relocate(FullName, .after = FamilyName)
  
        driverResult_GP <- rbind(driverResult_GP, result_temp)
      }
  
      driverResult <- rbind(driverResult, driverResult_GP)
  
      print(paste("Round", i, "of", latest_round, sep = " "))
  
      Sys.sleep(0.5)
    }
    
    driverResult <- driverResult[!duplicated(driverResult), ]
  
    saveRDS(driverResult, "data/driverResult2022.RDS")
    
    return(driverResult)
    
  } else {
    return(driverResult)
  }
  
}
```

```{r message=FALSE, warning=FALSE, include=FALSE}
getLapList <- function(latestRound = latest_round) {
  if(!file.exists("data/F1_lap_history2022.RDS")) {
    lap_list <- data.frame()
    max_round <- 1
  } else {
    lap_list <- readRDS("data/F1_lap_history2022.RDS")
    max_round <- (max(lap_list$Round)+1)
  }

  if(max_round <= latestRound) {
    for(j in max_round:round_var) {
      lap_list_temp <- data.frame()
      
      print(paste("Round", j, "of", round_var, sep = " "))
      
      for(i in 1:100) {
        url <- paste("https://ergast.com/api/f1/current/", j, "/laps/", i, sep = "")
        
        temp <- rawToChar(GET(url)$content)
        
        while(temp == "Unable to select database") {
          temp <- rawToChar(GET(url)$content)
        }
        
        temp <- xmlToList(temp)
        
        if(is.null(temp$RaceTable$Race$LapsList)) {
          break
        } else {
          lap_temp <- bind_rows(temp$RaceTable$Race$LapsList[[1]]) %>%
            select(-number)
          lap_list_temp <- rbind(lap_list_temp,lap_temp)
          
          print(paste("Lap", i))
          Sys.sleep(0.5)
        }
      }
      
      lap_list_temp$Round <- j
    }
    
    lap_list_temp <- lap_list_temp %>%
      drop_na()
    
    timeSecs_temp <- c()
    for (i in 1:length(lap_list_temp$time)) {
      timeSecs_temp <-c(timeSecs_temp,
      as.numeric(str_split(lap_list_temp$time[i], ":")[[1]][1]) * 60 + as.numeric(str_split(lap_list_temp$time[i], ":")[[1]][2])
      )
    }
    
    lap_list_temp <- lap_list_temp %>%
      mutate(position = as.numeric(position),lap = as.numeric(lap), timeSecs = timeSecs_temp) %>%
      left_join(
        driver_standings %>%
          select(driverId, Constructor, code)
      )
    
    lap_list <- rbind(lap_list, lap_list_temp)
    
    lap_list <- lap_list[!duplicated(lap_list), ]
    
    saveRDS(lap_list, "data/F1_lap_history2022.RDS")
    
    return(lap_list)
  } else {
    return(lap_list)
  }
}
```

```{r message=FALSE, warning=FALSE, include=FALSE}
getQualiResult <- function(latestRound = latest_round) {
  if(!file.exists("data/quali_results.RDS")) {
    quali_df <- data.frame()
    max_round <- 1
  } else {
    quali_df <- readRDS("data/quali_results.RDS")
    max_round <- (max(quali_df$Round)+1)
  }

  if(max_round <= latestRound) {
    for (j in max_round:round_var) {
      url <- paste("http://ergast.com/api/f1/current/", j, "/qualifying", sep = "")
      
      temp <- rawToChar(GET(url)$content)
      
      while(temp == "Unable to select database") {
        temp <- rawToChar(GET(url)$content)
      }
      
      temp <- xmlToList(temp)
      
      quali_ind <- temp$RaceTable$Race
      
      quali_temp <- data.frame()
      for(i in 1:length(quali_ind$QualifyingList)) {
        row_temp <- cbind(
          tibble(Round = j),
          tibble(
            FullName = paste(quali_ind$QualifyingList[i]$QualifyingResult$Driver["GivenName"], quali_ind$QualifyingList[i]$QualifyingResult$Driver["FamilyName"])
          ),
          bind_rows(quali_ind$QualifyingList[i]$QualifyingResult$Driver$.attrs["code"]),
          bind_rows(quali_ind$QualifyingList[i]$QualifyingResult$Driver["Nationality"]),
          bind_rows(quali_ind$QualifyingList[i]$QualifyingResult$Constructor["Name"]) %>% rename(Constructor = Name),
          if(is.null(quali_ind$QualifyingList[i]$QualifyingResult[["Q1"]])) {tibble(Q1 = NA)} else {
            bind_rows(quali_ind$QualifyingList[i]$QualifyingResult["Q1"])
          },
          if(is.null(quali_ind$QualifyingList[i]$QualifyingResult[["Q2"]])) {tibble(Q2 = NA)} else {
            bind_rows(quali_ind$QualifyingList[i]$QualifyingResult["Q2"])
          },
          if(is.null(quali_ind$QualifyingList[i]$QualifyingResult[["Q3"]])) {tibble(Q3 = NA)} else {
            bind_rows(quali_ind$QualifyingList[i]$QualifyingResult["Q3"])
          }
        )
        quali_temp <- rbind(quali_temp, row_temp)
      }
      quali_df <- rbind(quali_df, quali_temp)
      
      print(paste("Round", j, "of", latest_round, sep = " "))
      
      Sys.sleep(0.5)
    }
    
    quali_df <- quali_df[!duplicated(quali_df), ]
    
    saveRDS(quali_df, "data/quali_results.RDS")
    
    return(quali_df)
  } else {
    return(quali_df)
  }
}
```

```{r include=FALSE}
driver_standings <- getDriverStandings()

constructer_list <- unique(driver_standings %>% select(Constructor, ColorCode))

constructer_scale_colors <- getConstructerScaleColors()

lap_list <- getLapList(round_var)
driverResult <- getDriverResult(round_var)
quali_df <- getQualiResult(round_var)
```

```{r include=FALSE}
pointsLeft <- sum(grandPrixRounds$pointsFirst[grandPrixRounds$Round > latest_round])
pointsSecond <- sum(grandPrixRounds$pointsSecond[grandPrixRounds$Round > latest_round])
pointsThird <- sum(grandPrixRounds$pointsThird[grandPrixRounds$Round > latest_round])

prospectTable <- driver_standings %>%
  select(FullName,code,Constructor,position,points) %>%
  mutate(distToFirst = driver_standings$points[driver_standings$position==1] - points) %>%
  mutate(pointsMaximiz = pointsLeft - distToFirst) %>%
  mutate(pointsVsSecond = ifelse(
    position == 1, NA, pointsLeft - (distToFirst+pointsSecond)
  )) %>%
  mutate(pointsVsThird = ifelse(
    position == 1, NA, pointsLeft - (distToFirst+pointsThird)
  )) %>%
  rename(
    `distToFirst*` = distToFirst,
    `pointsMaximiz**` = pointsMaximiz,
    `pointsVsSecond***` = pointsVsSecond,
    `pointsVsThird****` = pointsVsThird
  )
```


## Grand Prix {-}

```{r echo=FALSE, fig.height=7, fig.width=9}
plotGPMap("Season")
```

## Calendar {-}

```{r echo=FALSE}
rownames(grandPrixRounds) <- c()

DT::datatable(
  grandPrixRounds %>%
  mutate(Date2 = format(as.Date(Date), format="%b %d")) %>%
  mutate(Date = Date2) %>%
  select(Round, RaceName, Date, CircuitName, Locality, Country),
options = list(pageLength = 25),
rownames= FALSE
)
```

## Current Driver Standings {-}

```{r echo=FALSE}
driver_standings_current <- driver_standings %>%
  select(FullName, code, PermanentNumber, Nationality, Constructor, position, points, wins) %>%
  rename(Num = PermanentNumber)

DT::datatable(driver_standings_current, options = list(pageLength = 25))
```

## Driver Points Development {-}

```{r include=FALSE}
driver_standings_season <- data.frame()
for(i in 1:latest_round) {
  driver_standings_current <- getDriverStandings(i, target_year) %>%
    mutate(Round = i) %>%
    select(Round, FullName, code, PermanentNumber, Nationality, Constructor, position, points, wins) %>%
    rename(Num = PermanentNumber)
  
  driver_standings_season <- rbind(driver_standings_season, driver_standings_current)
}
```

```{r echo=FALSE, fig.height=7, fig.width=9}
ggplotly(
    ggplot(driver_standings_season, aes(x = Round, y = points, fill = code, color = Constructor)) +
      geom_line() +
      constructer_scale_colors +
      labs(x = "Round", y = "Points", color = "Driver")
  )
```

## Position (WDC) Development {-}

```{r echo=FALSE, fig.height=7, fig.width=9}
ggplotly(
    ggplot(driver_standings_season, aes(x = Round, y = position, fill = code, color = Constructor)) +
      geom_line() +
      scale_y_continuous(trans = "reverse", breaks = unique(driver_standings_season$position)) +
      constructer_scale_colors +
      labs(x = "Round", y = "Position", color = "Driver")
  )
```

## Starting Position Development {-}

```{r echo=FALSE, fig.height=7, fig.width=9}
ggplotly(
    ggplot(driverResult, aes(x = Round, y = StartingPos, fill = code, color = Constructor)) +
      geom_line() +
      scale_y_continuous(trans = "reverse", breaks = unique(driverResult$StartingPos)) +
      constructer_scale_colors +
      labs(x = "Round", y = "Position", color = "Driver")
  )
```

## Championship forecast {-}

```{r echo=FALSE}
DT::datatable(
  prospectTable,
options = list(pageLength = 25)
)
```

<span style="font-size:12px">\*Distance to the driver in the first position, i.e. `r driver_standings$FullName[driver_standings$position==1]` (`r driver_standings$code[driver_standings$position==1]`).</span>  
<span style="font-size:12px">\*\*Points at the end of the season if driver wins the maximum amount of points available and `r driver_standings$code[driver_standings$position==1]` does not score a single point.</span>  
<span style="font-size:12px">\*\*\*Points at the end of the season if driver wins the maximum amount of points available and `r driver_standings$code[driver_standings$position==1]` achieves P2 in every remaining race (including sprint races).</span>  
<span style="font-size:12px">\*\*\*\*Points at the end of the season if driver wins the maximum amount of points available and `r driver_standings$code[driver_standings$position==1]` achieves P3 in every remaining race (including sprint races).</span>  