# <b>[Miami Grand Prix](http://en.wikipedia.org/wiki/2022_Miami_Grand_Prix)</b>

```{r warning=FALSE, include=FALSE}
library(f1Package)
lapply(f1_reqPackages, require, character.only = TRUE) 

Sys.setlocale("LC_TIME", "English")
```

```{r include=FALSE}
round_var <- 5

paste("# <b>[", grandPrixRounds$RaceName[grandPrixRounds$Round == round_var], "](", grandPrixRounds$url[round_var], ")</b>", sep = "")

target_year <- 2022
```

```{r include=FALSE}
# Grand Prix Rounds
url <- "http://ergast.com/api/f1/current"

temp <- xmlToList(rawToChar(GET(url)$content))

grandPrixRounds <- data.frame()
for(i in 1:(length(temp$RaceTable)-1)) {
  circuit_temp <- temp$RaceTable[i]
  
  row_temp <- cbind(
    as.numeric(circuit_temp$Race$.attrs["round"]),
    bind_rows(circuit_temp$Race[c(1,3)]),
    circuit_temp$Race$Circuit$CircuitName,
    bind_rows(circuit_temp$Race$Circuit$Location[1:2]),
    bind_rows(circuit_temp$Race$Circuit$Location$.attrs),
    circuit_temp$Race$.attrs["url"]
  ) %>%
    rename(
      CircuitName = "circuit_temp$Race$Circuit$CircuitName",
      Round = "as.numeric(circuit_temp$Race$.attrs[\"round\"])",
      url = 'circuit_temp$Race$.attrs["url"]'
      )
  
  grandPrixRounds <- rbind(grandPrixRounds, row_temp)
}

grandPrixRounds <- grandPrixRounds %>%
  mutate(pointsFirst = ifelse(
    Locality %in% c(
      "Imola",
      "Spielberg",
      "São Paulo"
    ),
    32,
    26
  )) %>%
  mutate(pointsSecond = ifelse(
    Locality %in% c(
      "Imola",
      "Spielberg",
      "São Paulo"
    ),
    25,
    20
  )) %>%
  mutate(pointsThird = ifelse(
    Locality %in% c(
      "Imola",
      "Spielberg",
      "São Paulo"
    ),
    21,
    15
  )) %>%
  mutate(lat = as.numeric(lat), long = as.numeric(long))
```

```{r include=FALSE}
driver_standings <- getDriverStandings()

constructer_list <- unique(driver_standings %>% select(Constructor, ColorCode))

constructer_scale_colors <- getConstructerScaleColors()

lap_list <- getLapList(round_var)
driverResult <- getDriverResult(round_var)
quali_df <- getQualiResult(round_var)
```

```{r include=FALSE}
winner_hex <- constructer_list$ColorCode[constructer_list$Constructor == as.character(driverResult %>% filter(Round == round_var) %>% filter(position == 1) %>% select(Constructor))]
pole_hex <- constructer_list$ColorCode[constructer_list$Constructor == as.character(driverResult %>% filter(Round == round_var) %>% filter(StartingPos == 1) %>% select(Constructor))]
fastest_lap_hex <- constructer_list$ColorCode[constructer_list$Constructor == as.character(driverResult %>% filter(Round == round_var) %>% filter(FastestLap == min(FastestLap, na.rm = T)) %>% select(Constructor))]
```


**Winner:** <span style="background-color:`r winner_hex`;color:white">&nbsp;`r paste(as.character(driverResult %>% filter(Round == round_var) %>% filter(position == 1) %>% select(code)), " (", as.character(driverResult %>% filter(Round == round_var) %>% filter(position == 1) %>% select(Constructor)), ")", sep = "")`&nbsp;</span> <br>

**Pole:** <span style="background-color:`r pole_hex`;color:white">&nbsp;`r paste(as.character(driverResult %>% filter(Round == round_var) %>% filter(StartingPos == 1) %>% select(code)), " (", as.character(driverResult %>% filter(Round == round_var, StartingPos == 1) %>% select(Constructor)), ")", sep = "")`&nbsp;</span>  <br>

**Fastest Lap:** <span style="background-color:`r fastest_lap_hex`;color:white">&nbsp;`r paste(as.character(driverResult %>% filter(Round == round_var) %>% filter(FastestLap == min(FastestLap, na.rm = T)) %>% select(code)), " (", as.character(driverResult %>% filter(Round == round_var) %>% filter(FastestLap == min(FastestLap, na.rm = T)) %>% select(Constructor)), ") - ", as.character(driverResult %>% filter(Round == round_var) %>% filter(FastestLap == min(FastestLap, na.rm = T)) %>% select(FastestLap)), "s", sep = "")`&nbsp;</span>

```{r echo=FALSE}
driver_standings <- getDriverStandings(round_var, target_year)

driver_standings_current <- driver_standings %>%
  select(FullName, code, PermanentNumber, Nationality, Constructor, position, points, wins) %>%
  rename(Num = PermanentNumber) %>%
  relocate(position, .before = FullName)
```

## Location

```{r echo=FALSE, fig.height=7, fig.width=9}
plotGPMap(round_var)
```

## Race Result

```{r echo=FALSE}
DT::datatable(
driverResult %>%
  filter(Round == round_var) %>%
  select(code, FullName, Constructor, position, StartingPos, points, Laps, Status, FastestLap, avgSpeedKph), 
options = list(pageLength = 25)
)
```

## Qualifying Results

```{r echo=FALSE}
DT::datatable(
quali_df[quali_df$Round == round_var,] %>% select(-c("Round", "Nationality")),
options = list(pageLength = 25)
)
```

## Track Position Development

```{r echo=FALSE, fig.height=7, fig.width=9}
lapPlots <- plotLapTimes(round_var)

lapPlots[[1]]
```

## Lap Time Development

```{r echo=FALSE, fig.height=7, fig.width=9}
lapPlots[[2]]
```

## WDC Standings

```{r echo=FALSE}
DT::datatable(driver_standings_current, options = list(pageLength = 25), rownames = F)
```